eu-circle-torbay-precip.Rmd

### 2016-12-08 EU-Circle/eu-circle_torbay-precip.Rmd

```{r trend}
## The area mean wet-day mean precipitation
plot(mu,new=FALSE)
grid()
lines(trend(mu),lty=2)
## The area mean wet-day frequency
plot(fw,new=FALSE)
grid()
lines(trend(mu),lty=2)
## The early part of the record looks suspect:
mu <- subset(mu,it=c(1958,2015))
fw <- subset(fw,it=c(1958,2015))
## Show maps of trends for the wet-day mean precipitation
map(mu,FUN='trend',
    colbar=list(breaks=seq(-0.12,0.12,by=0.02),pal='t2m',rev=TRUE))
## Map of trends in wet-day frequency:
map(fw,FUN='trend',
    colbar=list(breaks=seq(-0.01,0.01,by=0.001),pal='t2m',rev=TRUE))
```

>>>>

```{r trend}
## The area mean wet-day mean precipitation
plot(mu,new=FALSE)
grid()
#lines(trend(mu),lty=2)
## The area mean wet-day frequency
plot(fw,new=FALSE)
grid()
#lines(trend(fw),lty=2)
## The early part of the record looks suspect:
mu <- subset(mu,it=c(1958,2015))
fw <- subset(fw,it=c(1958,2015))
## Show maps of trends for the wet-day mean precipitation
map(mu,FUN='trend',
    colbar=list(breaks=seq(-0.12,0.12,by=0.02),pal='t2m',rev=TRUE))
## Map of trends in wet-day frequency:
map(fw,FUN='trend',
    colbar=list(breaks=seq(-0.01,0.01,by=0.001),pal='t2m',rev=TRUE))
```
